Paper_analyses

### 2021-09-01 IAPS_PREPROCESSING_2021_1.Rmd
HR analysyes
started the actual HR models

unique(tmp.df4_sum_full_bio_hr_self$ssid)
table(is.na(tmp.df4_sum_full_bio_hr_self$Mean_HR))
tmp.df4_sum_full_bio_hr_self <- left_join(tmp.df4_sum_full_bio_hr, db_selfrep, by = 'ssid')

write_csv(tmp.df4_sum_full, 'tmp.df4_sum_full_bio_hr_self_345_356.csv')

@@

>>>>

unique(tmp.df4_sum_full_bio_hr_self$ssid)
table(is.na(tmp.df4_sum_full_bio_hr$Mean_HR))

tmp.df4_sum_full_bio_hr_self <- left_join(tmp.df4_sum_full_bio_hr, db_selfrep, by = 'ssid')
table(is.na(tmp.df4_sum_full_bio_hr_self$Mean_HR))
write_csv(tmp.df4_sum_full, 'tmp.df4_sum_full_bio_hr_self_345_356.csv')

@@

tmp.df4_sum_full_bio_hr_self_parsed
table(is.na(tmp.df4_sum_full_bio_hr_self_parsed$Mean_HR))

### 2021-09-01 Paper_Analyses_subj_obje_arousal.Rmd
HR analysyes
started the actual HR models

db_HR_bio_final_346_355_withfix <-  read_csv("tmp.df4_sum_full_bio_hr_self_parsed_345_356.csv")
View(db_HR_bio_final_346_355_withfix)

@@

# 
db_HR_bio_final_346_355_withfix_stim$tNo<- db_HR_bio_final_346_355_withfix_stim$tNo3
unique(db_HR_bio_final_346_355_withfix$tNo)
unique(db_HR_bio_final_346_355_withfix$tNo)

@@

# keep controls
unique(db_full6new_hr_fix_stim$ssid)
db_full6new_hr_fix_stim$ssid_num <- as.numeric(as.character(db_full6new_hr_fix_stim$ssid))

@@

db_full6new_hr_fix_stim_nt<- subset(db_full6new_hr_fix_stim, ssid_num> 303)
unique(db_full6new_hr_fix_stim_nt$ssid)
colnames(db_full6new_hr_fix_stim_nt)
# HR differences
db_full6new_hr_fix_stim_nt$Bio_Mean_HR_fix<- if_else(db_full6new_hr_fix_stim_nt$screencontent_no ==1, db_full6new_hr_fix_stim_nt$Bio_Mean_HR, NULL)

@@

db_HR_bio_final_346_355_withfix_stim$triger<- NULL
db_HR_bio_final_346_355_withfix_stim$trigger.x<- NULL

@@

db_HR_bio_final_346_355_withfix_stim$stim<- db_HR_bio_final_346_355_withfix_stim$stim.x
db_HR_bio_final_346_355_withfix_stim$stim<- db_HR_bio_final_346_355_withfix_stim$stim.x

# bind heartrate old and new

@@

table(is.na(db_HR_bio_final_346_355_withfix_stim$Bio_Mean_HR))
table(is.na(db_full6new_hr_fix_stim_nt$Bio_Mean_HR))

@@

@@

db_full6new_hr_fix_stim_nt1.1<- db_full6new_hr_fix_stim_nt1.1 %>%
  mutate(Bio_Mean_HR_dif = Bio_Mean_HR - Bio_Mean_HR_fix)

# 2 1
stim - fix

@@

scatter3d(x = db_full6new_hr_fix_stim_nt1$pup_basCor, 
          y = db_full6new_hr_fix_stim_nt1$BIO_CDA.PhasicMax_z, 
          z = db_full6new_hr_fix_stim_nt1$Bio_Mean_HR_dif, 
          fit = "smooth",

          surface = FALSE,
          point.col = "blue",
          # point
          groups = as.factor(db_full6new_hr_fix_stim_nt1$mediansplit_ground_arousal),
          ellipsoid = TRUE)

@@

@@

```{r}
db_full6new_hr_fix_stim_nt1.1 %>%
    subset(Bio_Mean_HR_dif_outl == "not outlier")%>%
  subset(ssid_num<500)%>%
  group_by(ssid)%>%
  mutate(Bio_Mean_HR_dif_ssid = mean(Bio_Mean_HR_dif, na.rm = TRUE))%>%
  group_by(ssid)%>%
  # mutate(Bio_Mean_HR_dif_stim = mean(Bio_Mean_HR_dif, na.rm = TRUE))%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ggplot(aes(TAS, Bio_Mean_HR_dif))+
  geom_point()+
  geom_smooth(method = 'lm', se = F)+
  ggpubr::stat_cor()

db_full6new_hr_fix_stim_nt1.1 %>%
    subset(Bio_Mean_HR_dif_outl == "not outlier")%>%
  subset(ssid_num<500)%>%
  # group_by(ssid)%>%
  mutate(Bio_Mean_HR_dif = abs(Bio_Mean_HR_dif))%>%
  group_by(ssid, stimIAPS)%>%
  mutate(Bio_Mean_HR_dif_stim = abs(Bio_Mean_HR_dif))%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ggplot(aes(TASc, Bio_Mean_HR_dif))+

@@

subset(db_full6new_hr_fix_stim_nt1, Bio_Mean_HR_dif_outl == "not outlier")

@@

>>>>

# tmp.df4_sum_full_bio_hr_self_parsed_345_356.csv
db_HR_bio_final_346_355_withfix <-  read_csv("tmp.df4_sum_full_bio_hr_self_parsed_345_356.csv")
View(db_HR_bio_final_346_355_withfix)

@@

# 
# db_HR_bio_final_346_355_withfix_stim$tNo<- db_HR_bio_final_346_355_withfix_stim$tNo3
unique(db_HR_bio_final_346_355_withfix$tNo)
unique(db_HR_bio_final_346_355_withfix$tNo)

@@

db_HR_bio_final_346_355_withfix_stim$ssid_num<- as.numeric(db_HR_bio_final_346_355_withfix_stim$ssid)
# keep controls
unique(db_full6new_hr_fix_stim$ssid)
db_full6new_hr_fix_stim$ssid_num <- as.numeric(as.character(db_full6new_hr_fix_stim$ssid))

table(is.na(db_full6new_hr_fix_stim))

db_full6new_hr_fix_stim$Group<- if_else(db_full6new_hr_fix_stim$ssid_num< 500, "NT",
                                        if_else(db_full6new_hr_fix_stim$ssid_num>700, "NT",
                                                "ASC"))

table(is.na(db_full6new_hr_fix_stim$Group))

@@

# attention
db_full6new_hr_fix_stim_nt<- subset(db_full6new_hr_fix_stim_nt, ssid_num> 303)
unique(db_full6new_hr_fix_stim_nt$ssid)
colnames(db_full6new_hr_fix_stim_nt)

# HR differences
db_full6new_hr_fix_stim_nt$Bio_Mean_HR_fix<- if_else(db_full6new_hr_fix_stim_nt$screencontent_no ==1, db_full6new_hr_fix_stim_nt$Bio_Mean_HR, NULL)

@@

# db_HR_bio_final_346_355_withfix_stim$triger<- NULL
db_HR_bio_final_346_355_withfix_stim$trigger.x<- NULL

@@

db_HR_bio_final_346_355_withfix_stim$stim<- db_HR_bio_final_346_355_withfix_stim$stim.x
# db_HR_bio_final_346_355_withfix_stim$stim<- db_HR_bio_final_346_355_withfix_stim$stim.x

# bind heartrate old and new
table(is.na(db_HR_bio_final_346_355_withfix_stim$Bio_Mean_HR))
table(is.na(db_full6new_hr_fix_stim_nt$Bio_Mean_HR))
test<- subset(db_full6new_hr_fix_stim_nt, is.na(Bio_Mean_HR))
test1<- subset(db_HR_bio_final_346_355_withfix_stim, is.na(Bio_Mean_HR))

@@

unique(db_full6new_hr_fix_stim_nt$Group)

# 346 missing praticdata - it was processed wrongly
# 347 missing

@@

# 348 to 355 are missing pratice

@@

# 2 1
# stim - fix
db_full6new_hr_fix_stim_nt1.1<- db_full6new_hr_fix_stim_nt1.1 %>%
  mutate(Bio_Mean_HR_dif = Bio_Mean_HR - Bio_Mean_HR_fix)

@@

car::scatter3d(x = db_full6new_hr_fix_stim_nt1.1$pup_basCor, 
          y = db_full6new_hr_fix_stim_nt1.1$BIO_CDA.PhasicMax_z, 
          z = db_full6new_hr_fix_stim_nt1.1$Bio_Mean_HR_dif, 
          fit = "smooth",

          surface = FALSE,
          point.col = "blue",
          # point
          groups = as.factor(db_full6new_hr_fix_stim_nt1.1$mediansplit_ground_arousal),
          ellipsoid = TRUE)

@@

unique(test$ssid)

@@

db_full6new_hr_fix_stim_nt1.1<- db_full6new_hr_fix_stim_nt1.1%>%
  ungroup()%>%
  mutate(arousal_c = scale(arousal, center = TRUE, scale = TRUE)[,1],
         valence_c = scale(valence, center = TRUE, scale = TRUE)[,1])

db_full6new_hr_fix_stim_nt1.1 %>%
    # subset(Bio_Mean_HR_dif_outl == "not outlier")%>%
  # subset(ssid_num<500)%>%
  group_by(ssid)%>%
  mutate(Bio_Mean_HR_dif_ssid = mean(Bio_Mean_HR_dif, na.rm = TRUE))%>%
  group_by(ssid)%>%
  # mutate(Bio_Mean_HR_dif_stim = mean(Bio_Mean_HR_dif, na.rm = TRUE))%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ggplot(aes(TAS, Bio_Mean_HR_dif))+
  geom_point()+
  geom_smooth(method = 'lm', se = F)+
  ggpubr::stat_cor()

db_full6new_hr_fix_stim_nt1.1 %>%
    subset(Bio_Mean_HR_dif_outl == "not outlier")%>%
  # subset(ssid_num<500)%>%
  # group_by(ssid)%>%
  mutate(Bio_Mean_HR_dif = abs(Bio_Mean_HR_dif))%>%
  group_by(ssid, stimIAPS)%>%
  mutate(Bio_Mean_HR_dif_stim = abs(Bio_Mean_HR_dif))%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ggplot(aes(TASc, Bio_Mean_HR_dif))+

@@

# create more variables ground and self
db_full6new_hr_fix_stim_nt1.1<- db_full6new_hr_fix_stim_nt1.1%>%
  ungroup()%>%
  mutate(mediansplit_ground_valence = if_else(ValenceMean >=
                                                  median(ValenceMean,
                                                         na.rm = TRUE), "More positive", "More negative"))%>%
  mutate(mediansplit_ground_arousal = if_else(ArousalMean >=
                                                  median(ArousalMean,
                                                         na.rm = TRUE), "High", "Low"))%>%
    mutate(mediansplit_sample_valence2 = if_else(valence >=
                                                  median(valence,
                                                         na.rm = TRUE), "More positive", "More negative"))%>%
  mutate(mediansplit_sample_arousal2 = if_else(arousal >=
                                                  median(arousal,
                                                         na.rm = TRUE), "High", "Low"))

db_full6new_hr_fix_stim_nt1.1%>%
  subset(Bio_Mean_HR_dif_outl == "not outlier")%>%
  subset(!is.na(mediansplit_ground_valence))%>%
  group_by(ssid,mediansplit_ground_arousal, mediansplit_ground_valence,)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ggplot(aes(mediansplit_ground_arousal, Bio_Mean_HR_dif))+
  geom_jitter(alpha = .2, width = .2)+
   geom_bar(stat="summary", fun.y = "mean", alpha = .2)+
  stat_summary(geom = 'pointrange')+
  # stat_smooth(aes(group = ssid), se = F, method = 'lm', alpha = .2)+
    facet_grid(~mediansplit_ground_valence)

@@

```{r}
db_full6new_hr_fix_stim_nt1.1%>%
  subset(!is.na(mediansplit_ground_valence))%>%
  subset(Bio_Mean_HR_dif_outl== "not outlier")%>%
  group_by(ssid, mediansplit_ground_arousal,mediansplit_ground_valence)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ggplot(aes(mediansplit_ground_arousal, Bio_Mean_HR_dif, fill = mediansplit_ground_valence))+
  geom_jitter(alpha = .2, width = .2)+
   geom_bar(stat="summary", fun.y = "mean", alpha = .2)+
  stat_summary(geom = 'pointrange')+
  stat_summary(aes(group = ssid), geom = 'line', alpha = .2)+

  facet_grid(~mediansplit_ground_valence)+
     ggpubr::stat_compare_means()+
  # p$graphstyle+
  scale_fill_brewer(palette = "Dark2")

Models

```{r}
table(is.na(db_full6new_hr_fix_stim_nt1.1$Bio_Mean_HR_dif))
test3<- subset(db_full6new_hr_fix_stim_nt1.1, is.na(Bio_Mean_HR_dif))
test4<- subset(db_full6new_hr_fix_stim_nt1.1, !is.na(Bio_Mean_HR_dif))
unique(test4$ssid)

db_full6new_hr_fix_stim_nt1.1$ssid<- as.factor(as.character(db_full6new_hr_fix_stim_nt1.1$ssid))

db_full6new_hr_fix_stim_nt1.1<- db_full6new_hr_fix_stim_nt1.1%>%
  ungroup()%>%
  mutate(arousal_c = scale(arousal, center = TRUE, scale = TRUE)[,1],
         valence_c = scale(valence, center = TRUE, scale = TRUE)[,1])

unique(db_full6new_hr_fix_stim_nt1$Group)
# test - analyse just positive
summary(hr_dif_models$arousal_val)

hr_dif_models$arousal_val <- lmer(Bio_Mean_HR_dif ~   valence_c+
                                        + (1 | ssid) + 
                                    (1|stimIAPS),
                                        # (1|mediansplit_sample_arousal2),
     REML = FALSE,
     data = subset(db_full6new_hr_fix_stim_nt1.1, 
                   # mediansplit_ground_valence == "More negative" &
                     Bio_Mean_HR_dif_outl == "not outlier"))

summary(hr_dif_models$arousal_val)

summary(hr_dif_models$arousal_AR)

hr_outlier<- subset(db_full6new_hr_fix_stim_nt1.1, 
                   # mediansplit_ground_valence == "More negative" &
                     Bio_Mean_HR_dif_outl != "not outlier")

hr_dif_models$arousal_AR <- lmer(Bio_Mean_HR_dif ~   arousal_c+
                                        + (1 | ssid) + 
                                    (1|stimIAPS),
                                        # (1|mediansplit_sample_arousal2),
     REML = FALSE,
     data = subset(db_full6new_hr_fix_stim_nt1.1, 
                   # mediansplit_ground_valence == "More negative" &
                     Bio_Mean_HR_dif_outl == "not outlier"))

summary(hr_dif_models$arousal_AR)

unique(db_full6new_hr_fix_stim_nt1$ssid)

summary(hr_dif_models$valfrom_hr)

unique(db_full6new_hr_fix_stim_nt1.1$ssid)

hr_dif_models$valfrom_hr <- lmer(arousal_c ~   Bio_Mean_HR_dif* valence_c+
                                        + (1 | ssid) + (1|stimIAPS),
                                        # (1|mediansplit_sample_arousal2),
     REML = FALSE,
     data = subset(db_full6new_hr_fix_stim_nt1.1, 
                   # mediansplit_ground_valence == "More positive" &
                   Bio_Mean_HR_dif_outl == "not outlier"))
# arousal_c
summary(hr_dif_models$valfrom_hr)

# arousal * valence

hr_dif_models$hr_dif_ar_vl <- lmer(Bio_Mean_HR_dif~arousal_c   * valence_c+
                                        + (1 | ssid),
                                     # (1|stimIAPS),
                                        # (1|mediansplit_sample_arousal2),
     REML = FALSE,
     data = subset(db_full6new_hr_fix_stim_nt1.1, 
                   # mediansplit_ground_valence == "More positive" &
                   Bio_Mean_HR_dif_outl == "not outlier" & !is.na(Bio_Mean_HR_dif)))
# arousal_c
summary(hr_dif_models$hr_dif_ar_vl)
